High-order dynamic neural correlations reflect naturalistic processing in humans

### 2019-04-06 paper/main.tex
updated abstract

\title{An examination of the high-order dynamic interactions
  underlying multi-dimensional timeseries data} \author{Lucy
  L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
  Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
  [0.1in]$^1$Department of Psychological and Brain
  Sciences,\\Dartmouth
  College, Hanover, NH\\
  $^3$Amazon.com, Seattle, WA\\
  \textsuperscript{$\dagger$}Address correspondence to
  jeremy.r.manning@dartmouth.edu}

@@

\begin{abstract}
  Most complex systems reflect dynamic interactions between myriad
  evolving components (e.g., interacting molecules, interacting brain
  systems, interacting individuals within a social network or
  ecological system, coordinated components within a mechanical or
  digital device, etc.).  Despite that these interactions are central
  to the full system's behavior (e.g., removing a component from the
  full system can change the entire system's behavior), dynamic
  interactions cannot typically be directly measured.  Rather, the
  interactions must be inferred through their hypothesized role in
  guiding the dynamics of system components.  Here we use a
  model-based approach to inferring dynamic interactions from
  timeseries data.  In addition to examining first-order interactions
  (e.g., between pairs of components) we also examine higher-order
  interactions (e.g., that characterize mirrored structure in the
  patterns of interaction dynamics displayed by different subsets of
  components).  We apply our approach to two datasets.  First, we use
  a synthetic dataset, for which the underlying dynamic interactions
  are known, to show that our model recovers those ground-truth
  dynamic interactions.  We also apply our model to a neuroimaging
  dataset and show that the high-order dynamic interactions exhibited
  by brain data vary meaningfully as a function of the cognitive
  ``richness'' of the stimulus people are experiencing.
\end{abstract}

>>>>

\title{High-order dynamic neural correlations reflect naturalistic processing
in humans} \author{Lucy
  L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
  Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
  [0.1in]$^1$Department of Psychological and Brain
  Sciences,\\Dartmouth
  College, Hanover, NH\\
  $^3$Amazon.com, Seattle, WA\\
  \textsuperscript{$\dagger$}Address correspondence to
  jeremy.r.manning@dartmouth.edu}

@@

\begin{abstract}
  Our thoughts arise from coordinated activity patterns across our
  brain.  We examined high-order dynamic correlations in functional
  neuroimaging data collect as human participants listened to
  different auditory stimuli varying in cognitive richness, along with
  an additional resting state condition.  Our approach combines a
  kernel-based method for estimating the dynamic functional
  correlations that are similar (within task) across participants,
  along with a dimensionality reduction approach that enables us to
  efficiently compute high-order correlations in the data.  We trained
  classifiers to decode the precise time, relative to the start of the
  stimulus, when a given neural pattern was recorded.  We trained
  these classifiers using the neural activity timeseries, first-order
  dynamic correlations, and higher-order correlations (up to
  tenth-order correlations), and asked which types of features led to
  the highest decoding accuracy.  We found that second-order
  correlations consistently yielded the highest decoding accuracy in
  all of the listening conditions of the experiment, whereas
  first-order correlations yielded the highest decoding accuracy at
  rest.
\end{abstract}
